Information and Airbnb, An Analysis on the Impact of Reviews and Ratings on Airbnb Prices in Canada

### 2024-02-14 outputs/paper.qmd
Added graphs to qmd.

---
title: "The Impact of Urbanization, Culture, and Wealth on Public Art in Toronto"
author: 
  - Alaina Hu
thanks: "Code and data are available at: https://github.com/alainahu/public_art"
date: today
date-format: long
abstract: "Public art has emerged in many urban cities across the world. Existing research and analysis on public art often focuses on the impact of public art on various factors, making public art the explanatory variable. This paper examines public art as a response variable to explanatory variables such as population, minority population, and income as a measure of urbanization, culture, and wealth respectively with Public Art Data and Ward Data for the city of Toronto. Through data visualization, we find a moderately positive relationship between population and public art but no relationship between minority population and public art or income and public art."
format: pdf
toc: true
number-sections: true
#bibliography: references.bib
---

>>>>

---
title: "Information and Airbnb, An Analysis on the Impact of Reviews and Ratings on Airbnb Prices in Canada"
author: 
  - Alaina Hu and Ahad Qureshi
thanks: "Code and data are available at: https://github.com/alainahu/airbnb_analysis"
date: today
date-format: long
abstract: ''
format: pdf
toc: true
number-sections: true
#bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(knitr)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(RColorBrewer)
library(gridExtra)
```
# Introduction

# Data

```{r}
#| echo: false
airbnb <- read_csv("~/airbnbtp2/inputs/data/airbnb_cleaned_data.csv")
```

```{r}
#| fig-cap: Distribution of Airbnb prices per night (including cleaning fees)
#| label: price_dist
#| echo: false

df1 <- airbnb
ggplot(df1, aes(x=new_price)) +
  geom_histogram(aes(y=..density..), binwidth=10, colour="black", fill="grey") + # binwidth adjusted for demonstration
  scale_x_continuous(limits=c(0, 500), breaks=seq(0, 500, by=50), name="Price") +
  scale_y_continuous(name="Density") +
  theme_minimal() +
  theme(plot.background = element_rect(fill="white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust=0.5))

summary(df1$new_price)
```

```{r}
summary_df <- airbnb |>
  summarise(
    Mean_New_Price = mean(new_price, na.rm = TRUE),
    Median_New_Price = median(new_price, na.rm = TRUE),
    SD_New_Price = sd(new_price, na.rm = TRUE))
```

```{r}
```

```{r}
#| tbl-cap: Summary Statistics for the Reviews and Ratings 
#| label: summ_stats
#| echo: false

summary <- airbnb |>
  summarise(
    Mean_Review = mean(review, na.rm = TRUE),
    Median_Review = median(review, na.rm = TRUE),
    SD_Review = sd(review, na.rm = TRUE),
    Min_Review = min(review, na.rm = TRUE),
    Max_Review = max(review, na.rm = TRUE),
    Mean_Guest = mean(guest_satisfaction_overall, na.rm = TRUE),
    Median_Guest = median(guest_satisfaction_overall, na.rm = TRUE),
    SD_Guest = sd(guest_satisfaction_overall, na.rm = TRUE),
    Min_Guest = min(guest_satisfaction_overall, na.rm = TRUE),
    Max_Guest = max(guest_satisfaction_overall, na.rm = TRUE),
    Mean_Accuracy = mean(accuracy_rating, na.rm = TRUE),
    Median_Accuracy = median(accuracy_rating, na.rm = TRUE),
    SD_Accuracy = sd(accuracy_rating, na.rm = TRUE),
    Min_Accuracy = min(accuracy_rating, na.rm = TRUE),
    Max_Accuracy = max(accuracy_rating, na.rm = TRUE),
    Mean_Clean = mean(cleanliness_rating, na.rm = TRUE),
    Median_Clean = median(cleanliness_rating, na.rm = TRUE),
    SD_Clean = sd(cleanliness_rating, na.rm = TRUE),
    Min_Clean = min(cleanliness_rating, na.rm = TRUE),
    Max_Clean = max(cleanliness_rating, na.rm = TRUE),
    Mean_Location = mean(location_rating, na.rm = TRUE),
    Median_Location = median(location_rating, na.rm = TRUE),
    SD_Location = sd(location_rating, na.rm = TRUE),
    Min_Location = min(location_rating, na.rm = TRUE),
    Max_Location = max(location_rating, na.rm = TRUE),
    Mean_Value = mean(value_rating, na.rm = TRUE),
    Median_Value = median(value_rating, na.rm = TRUE),
    SD_Value = sd(value_rating, na.rm = TRUE),
    Min_Value = min(value_rating, na.rm = TRUE),
    Max_Value = max(value_rating, na.rm = TRUE)
  )
long_summary_stats <- summary |>
  pivot_longer(cols = everything(), names_to = "Statistic", values_to = "Value") |>
  separate(Statistic, into = c("Measure", "Variable"), sep = "_") |>
  spread(key = Measure, value = Value) |>
  select(Variable, Mean, Median, SD, Min, Max)

long_summary_stats$Variable <- c("Accuracy Rating", "Cleanliness Rating", "Guest Overall Satisfaction", 
                                 "Location Rating", "Number of Reviews", "Value Rating")

# Now use kable to create the markdown table
kable(long_summary_stats, 
      format = "markdown", 
      digits = 2,
      col.names = c("Variable", "Mean", "Median", "Standard Deviation", "Min", "Max"),
      row.names = FALSE, # We already have the Variable column, so we don't want to print row names
      align = c('l', 'r', 'r', 'r', 'r', 'r'), # Align the columns left for variable name and right for numbers 
      )

```
```{r}
#| echo: false
set2Colors <- brewer.pal(8, "Set2")
toronto <- set2Colors[1] # Light green
vancouver <- set2Colors[2]
```

```{r}
#| tbl-cap: Plot of Listing Reviews and Price
#| label: review_price
#| echo: false
#| 
ggplot(airbnb, aes(x = review, y = new_price, color = city)) +
         geom_point(size = 0.75) +
         geom_smooth(aes(color = city), method = "lm", se = FALSE, size = 1.5) +        geom_smooth(method = "lm", color = "black", se = TRUE, size = 1) +  
         labs(
       x = "Number of Reviews", 
       y = "Price") +
  theme_minimal() +
  theme(plot.background = element_rect(color = "black", fill = "white"))
  scale_color_brewer(palette = "Set2")
```

```{r}
#| tbl-cap: Plot of Guest Overall Satisfaction Score and Price
#| label: guest_satisf
#| echo: false
#| 
ggplot(airbnb, aes(x = guest_satisfaction_overall, y = new_price, color = city)) +
         geom_point(size = 0.75) +
         geom_smooth(aes(color = city), method = "lm", se = FALSE, size = 1.5) +        geom_smooth(method = "lm", color = "black", se = TRUE, size = 1) +  
         labs(
       x = "Guest Overall Satisfaction Score", 
       y = "Price") +
  theme_minimal() +
  theme(plot.background = element_rect(color = "black", fill = "white")) 
  scale_color_manual(values = c("toronto" = toronto, "vancouver" = vancouver))
```

```{r}
unique_values <- unique(airbnb$accuracy_rating)

# Print the unique values
print(unique_values)
```

```{r}
#| tbl-cap: Plot of Accuracy Rating and Price
#| label: accuracy_price
#| echo: false

ggplot(airbnb, aes(x=factor(accuracy_rating), y=new_price)) +
  geom_violin(trim=FALSE, fill="grey") +
  stat_summary(fun=mean, geom="point", shape=23, size=2, fill="white") +
  scale_x_discrete(limits = as.character(0:10)) + 
  labs(x = "Accuracy Rating", y = "Price") +
  theme_minimal()

```

```{r}
#| echo: false
toronto_data <- airbnb |>
  filter(city == "toronto")

toronto_accuracy <- ggplot(toronto_data, aes(x=factor(accuracy_rating), y=new_price)) +
  geom_violin(trim=FALSE, fill=toronto) +
  stat_summary(fun=mean, geom="point", shape=23, size=2, fill="white") +
  scale_x_discrete(limits = as.character(0:10)) + 
  labs(x = "Accuracy Rating", y = "Price") +
  theme_minimal()
```

```{r}
#| echo: false
vancouver_data <- airbnb |>
  filter(city == "vancouver")

vancouver_accuracy <- ggplot(vancouver_data, aes(x=factor(accuracy_rating), y=new_price)) +
  geom_violin(trim=FALSE, fill=vancouver) +
  stat_summary(fun=mean, geom="point", shape=23, size=2, fill="white") +
  scale_x_discrete(limits = as.character(0:10)) + 
  labs(x = "Accuracy Rating", y = "Price") +
  theme_minimal()
```

```{r}
#| tbl-cap: Plot of Accuracy Rating and Price in Toronto (left) and Vancouver (right)
#| label: accuracy_price_2
#| echo: false
grid.arrange(toronto_accuracy, vancouver_accuracy, ncol = 2)
```

```{r}
#| tbl-cap: Plot of Cleanliness Rating and Price
#| label: clean_price
#| echo: false

ggplot(airbnb, aes(x=factor(cleanliness_rating), y=new_price)) +
  geom_violin(trim=FALSE, fill="grey") +
  stat_summary(fun=mean, geom="point", shape=23, size=2, fill="white") +
  scale_x_discrete(limits = as.character(0:10)) + 
  labs(x = "Cleanliness Rating", y = "Price") +
  theme_minimal()

```

```{r}
#| echo: false

toronto_cleanliness <- ggplot(toronto_data, aes(x=factor(cleanliness_rating), y=new_price)) +
  geom_violin(trim=FALSE, fill=toronto) +
  stat_summary(fun=mean, geom="point", shape=23, size=2, fill="white") +
  scale_x_discrete(limits = as.character(0:10)) + 
  labs(x = "Cleanliness Rating", y = "Price") +
  theme_minimal()
```

```{r}
#| echo: false

vancouver_cleanliness <- ggplot(vancouver_data, aes(x=factor(cleanliness_rating), y=new_price)) +
  geom_violin(trim=FALSE, fill=vancouver) +
  stat_summary(fun=mean, geom="point", shape=23, size=2, fill="white") +
  scale_x_discrete(limits = as.character(0:10)) + 
  labs(x = "Cleanliness Rating", y = "Price") +
  theme_minimal()
```

```{r}
#| tbl-cap: Plot of Cleanliness Rating and Price in Toronto (left) and Vancouver (right)
#| label: clean_price_2
#| echo: false
grid.arrange(toronto_cleanliness, vancouver_cleanliness, ncol = 2)
```

```{r}
#| tbl-cap: Plot of Location Rating and Price
#| label: location_price
#| echo: false

ggplot(airbnb, aes(x=factor(location_rating), y=new_price)) +
  geom_violin(trim=FALSE, fill="grey") +
  stat_summary(fun=mean, geom="point", shape=23, size=2, fill="white") +
  scale_x_discrete(limits = as.character(0:10)) + 
  labs(x = "Location Rating", y = "Price") +
  theme_minimal()

```

```{r}
#| echo: false

toronto_location <- ggplot(toronto_data, aes(x=factor(location_rating), y=new_price)) +
  geom_violin(trim=FALSE, fill=toronto) +
  stat_summary(fun=mean, geom="point", shape=23, size=2, fill="white") +
  scale_x_discrete(limits = as.character(0:10)) + 
  labs(x = "Location Rating", y = "Price") +
  theme_minimal()
```

```{r}
#| echo: false

vancouver_location <- ggplot(vancouver_data, aes(x=factor(location_rating), y=new_price)) +
  geom_violin(trim=FALSE, fill=vancouver) +
  stat_summary(fun=mean, geom="point", shape=23, size=2, fill="white") +
  scale_x_discrete(limits = as.character(0:10)) + 
  labs(x = "Location Rating", y = "Price") +
  theme_minimal()
```

```{r}
#| tbl-cap: Plot of Location Rating and Price in Toronto (left) and Vancouver (right)
#| label: location_price_2
#| echo: false
grid.arrange(toronto_location, vancouver_location, ncol = 2)
```

```{r}
#| tbl-cap: Plot of Value Rating and Price
#| label: value_price
#| echo: false

ggplot(airbnb, aes(x=factor(value_rating), y=new_price)) +
  geom_violin(trim=FALSE, fill="grey") +
  stat_summary(fun=mean, geom="point", shape=23, size=2, fill="white") +
  scale_x_discrete(limits = as.character(0:10)) + 
  labs(x = "Value Rating", y = "Price") +
  theme_minimal()

```

```{r}
#| echo: false

toronto_value <- ggplot(toronto_data, aes(x=factor(value_rating), y=new_price)) +
  geom_violin(trim=FALSE, fill=toronto) +
  stat_summary(fun=mean, geom="point", shape=23, size=2, fill="white") +
  scale_x_discrete(limits = as.character(0:10)) + 
  labs(x = "Value Rating", y = "Price") +
  theme_minimal()
```

```{r}
#| echo: false

vancouver_value <- ggplot(vancouver_data, aes(x=factor(value_rating), y=new_price)) +
  geom_violin(trim=FALSE, fill=vancouver) +
  stat_summary(fun=mean, geom="point", shape=23, size=2, fill="white") +
  scale_x_discrete(limits = as.character(0:10)) + 
  labs(x = "Value Rating", y = "Price") +
  theme_minimal()
```

```{r}
#| tbl-cap: Plot of Value Rating and Price in Toronto (left) and Vancouver (right)
#| label: value_price_2
#| echo: false
grid.arrange(toronto_value, vancouver_value, ncol = 2)
```
